---
title: "semi-supervised-ML4MI Repository \U0001F916"
output:
  html_document:
    df_print: paged
---

This is the repository of Semi-supervised machine learning classification framework for material intensity parameters of residential buildings.

Citation : Preprint -->> Vilaysouk, Xaysackda & Saypadith, Savath & Hashimoto, Seiji. (2020). Semi-supervised machine learning classification framework for material intensity parameters of residential buildings. DOI:10.13140/RG.2.2.16267.11048.

```{r, error=FALSE , warning=FALSE}
library(readxl)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(plotly)
library(reshape2)
library(factoextra)
library(NbClust)
library(cluster)
library(mclust)
library(ggpubr)
```

Pre-processing Dataset
```{r, error=FALSE , warning=FALSE}
data_mod <- read_csv("./MI.v2.csv") %>% filter(Occupation == "residential") %>%
  filter(total >100) ## @ filter only residential building

# select main material categories
data_selected <- data_mod %>% dplyr::select (metal_based,biomass_based,cca,other_construction_materials, total)

#adjust NA value as mean value
for(i in 1:5){
  data_selected[is.na(data_selected[,i]), i] <- mean(as.matrix(na.omit(data_selected[,i])))
}

#adjust dataset scale for k-mean
data_for_kmean <- scale(data_selected)
head(data_for_kmean)
```

Find optimal k using traditional approaches 
```{r}
#Elbow Method
fviz_nbclust(data_for_kmean ,kmeans, method = "wss") + ggtitle("Optimal number for k of the MI parameters")

#Silhouette Method
fviz_nbclust(data_for_kmean ,kmeans, method = "silhouette") + ggtitle("Optimal number for k of the MI parameters silhouette")

set.seed(123)
gap_stat <- clusGap(data_for_kmean, FUN = kmeans, nstart = 25,
                    K.max = 10, B = 50)
#Gap Statistic Method
fviz_gap_stat(gap_stat)
```

Find the optimal number of k by comparing other indexes using NbClust package
```{r}
res.nbclust <- NbClust(data_for_kmean, distance = "euclidean",
                  min.nc = 2, max.nc = 10, 
                  method = "kmeans", index ="all")
factoextra::fviz_nbclust(res.nbclust) + theme_minimal() + ggtitle("NbClust's optimal number of clusters")
```

Un-supervised Machine Learning models for different k value
```{r}
## run for difference k value ##
set.seed(1)
k4 <- kmeans(data_for_kmean, 4, nstart = 30) ## k = 4
set.seed(1)
k5 <- kmeans(data_for_kmean, 5, nstart = 30) ## k = 5
set.seed(1)
k6 <- kmeans(data_for_kmean, 6, nstart = 30) ## k = 6
set.seed(1)
k7 <- kmeans(data_for_kmean, 7, nstart = 30) ## k = 7

## plot clustering result in 2 dimensions using PCA to reduce number of dimention ##
p1 <- fviz_cluster(k4, geom = "point" , data_for_kmean) + ggtitle("k=4")
p2 <- fviz_cluster(k5, geom = "point" , data_for_kmean) + ggtitle("k=5")
p3 <- fviz_cluster(k6, geom = "point" , data_for_kmean) + ggtitle("k=6")
p4 <- fviz_cluster(k7, geom = "point" , data_for_kmean) + ggtitle("k=7") 
p1
p2
p3
p4

```
Create new dataset for un-supervised machine learning model
```{r}
data_trained <- cbind(data_mod, cluster = k7$cluster) 
data_trained$label <- toupper(data_trained$label)
```


Install for first time
```{r}
# install.packages('e1071', dependencies=TRUE)
```

Libraries for Supervised ML part
```{r warning=FALSE}
library(party)
library(ggparty)
library(caret)
```


```{r warning=FALSE}
boxPlotMI <- data_trained %>% dplyr::select(Metal = metal_based, Biomass = biomass_based, CCA = cca, Brick = other_construction_materials,cluster,Total = total) %>% melt(id="cluster") %>% ggplot( aes(x = variable, y = value)) + geom_boxplot(aes(color = as.factor(cluster), fill = as.factor(cluster), alpha = 0.7),width = 0.3) + facet_wrap( ~ cluster, scales = "free") + labs(x = "", y = "MI: Material Intensity (kg/m²)") + guides(alpha = F, fill = F, color = F) + theme(axis.text=element_text(size=12), axis.title=element_text(size=14,face="bold")) 

simNo = Sys.Date()
#tiff(filename = paste("./plot/boxplotK7",simNo,".tiff"), width = 900, height = 900)
boxPlotMI
#dev.off()
```
Supervised Machine Learning Model
```{r warning=FALSE}
DT = data_trained 

# Save csv file for trained dataset with Cluster number 
#write.csv(DT, file = paste0("./",gsub(" ","",Sys.time()),"data_trained.csv"))

# Ignore Cluster 1 and Cluster 5 due to small number of samples
DT <-  DT %>% dplyr::filter(cluster != 5)
DT <-  DT %>% dplyr::filter(cluster != 1)

dt <- DT %>% dplyr::select(BDType  = building_type, BDMat = label, cluster, year = construction_period_start, Region = global_region, No_Floors = no_floors)


# Define building type
dt$BDType[is.na(dt$BDType)] <- "Type.NA"
dt$BDType[dt$BDType == "SFH, MFH"] <- "TypeMix"

# Define number of floor category
dt$No_Floors[is.na(dt$No_Floors)] <- "FlNA"
dt$No_Floors[dt$No_Floors >= 4] <- "FlH"
dt$No_Floors[dt$No_Floors < 4] <- "FlL"

# Define Material category for data points that not consist any information
dt$BDMat[is.na(dt$BDMat)] <- "MatNA"


# Define clusters based on main material information from k-mean interpretation 
dt$BDMat[dt$cluster == 2] <- "W"
dt$BDMat[dt$cluster == 3] <- "B"
dt$BDMat[dt$cluster == 4] <- "C"
dt$BDMat[dt$cluster == 6] <- "B-C"
dt$BDMat[dt$cluster == 7] <- "C"

#Set the interval for constrction period
dt$year[dt$year < 1901] <- "1870-1900"
dt$year[dt$year > 1900 | dt$year < 1931] <- "1901-1930"
dt$year[dt$year > 1930 | dt$year < 1961] <- "1931-1960"
dt$year[dt$year > 1960 | dt$year < 1991] <- "1961-1990"
dt$year[dt$year > 1990 | dt$year < 2011] <- "1991-2010"

#Shorten Variables names
dt$Region[dt$Region == "South_and_Southeast_Asia"] <- "SA"
dt$Region[dt$Region == "East_Asia"] <- "EA"
dt$Region[dt$Region == "Europe"] <- "EU"
dt$Region[dt$Region == "North_America"] <- "NAm"
dt$Region[dt$Region == "South_America"] <- "SAm"
dt$Region[dt$Region == "SIDS"] <- "SIs"

dt$Region <- paste("(",dt$Region, ")", sep = "")
dt$BDMat <- paste("(",dt$BDMat, ")", sep = "")
dt$BDType <- paste("(",dt$BDType, ")", sep = "")


#embedded C for Cluster
for (i in 1:7) {
  dt$cluster[dt$cluster == i] <- paste("C",i, sep = "")
}

#change data type to be factor type
for (i in 1:length(dt)) {
  dt[,i] <- as.factor(dt[,i])
}

# Split dataset for train set and test set
set.seed(1234)
ind <- sample(2, nrow(dt), replace = TRUE, prob = c(0.7,0.3)) #70% #30%

trainDT <- dt[ind==1,]
testDT <- dt[ind==2,]

```

```{r}
dtree <- ctree(cluster ~ ., data = trainDT)

#Plot Decision tree
t <- ggparty(dtree) +
  geom_edge(aes(col = factor(id)), guides(color = F)) +
  geom_edge_label(aes(col = factor(id))) +
  geom_node_label(aes(col = factor(id)),
    line_list = list(
      aes(label = splitvar),
      aes(label = paste("N =", nodesize))
    ),
    line_gpar = list(
      list(size = 12),
      list(size = 12)
    ),
    ids = "inner"
  ) +
  geom_node_label(aes(label = paste0("Node ", id, ", N = ", nodesize), col = factor(id)),
    ids = "terminal", nudge_y = 0.015, nudge_x = .02,
  ) +
  geom_node_plot(
    shared_legend = TRUE,
    gglist = list(geom_bar(aes(x = cluster,fill = cluster)),
                        xlab(""), ylab(""),
                  theme(legend.position = "none")),
  )+ theme(legend.position = "none")
t
```


The confusion matrix
```{r}
conFusm <- confusionMatrix(predict(dtree, testDT),testDT$cluster,dnn = c("Prediction", "Actual"))
conFusm
```

Plot of Confusion Matrix
```{r}
ggplot(as.data.frame(conFusm$table), aes(Prediction,sort(Actual,decreasing = T), fill= Freq)) +
  geom_tile() + geom_text(aes(label=Freq)) +
  scale_fill_gradient(low="white", high="blue") +
  labs(x = "Actual Clusters",y = "Prediction Clusters") +
  scale_x_discrete(labels=c("C2","C3","C4", "C6", "C7")) +
  scale_y_discrete(labels=c("C7","C6","C4", "C3", "C2"))

```


